14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Pass over first half of benchmarks section.

\header{Benchmark Selection.}
This track will run on all \emph{unsatisfiable} benchmarks from the \maintrack.

@@

@@

\header{Benchmark sources.}
%
Benchmarks for each division will be drawn from the SMT-LIB benchmark
library.  The \maintrack will use a subset of all
\emph{non-incremental} benchmarks; the incremental track will use a
subset of all \emph{incremental} benchmarks.  The \ucoretrack
will use unsatisfiable \maintrack benchmarks, modified to use named
top-level assertions.

\header{New benchmarks.}
%
The deadline for submission of new benchmarks is {\bf March~1, 2019}.
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf May~1, 2019}.  The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

\header{Benchmark demographics.}
%
The set of all SMT-LIB benchmarks in a given division can be naturally
partitioned to sets containing benchmarks that are similar from the user
community perspective.  Such benchmarks could all come from the same
application domain, be generated by the same tool, or have some other
obvious common identity.
%
The organizers try to identify a meaningful partitioning based on the
directory hierarchy in SMT-LIB.  In many cases the hierarchy consists of
the top-level directories each corresponding to a submitter, who has
further imposed a hierarchy on the benchmarks.
%
The organizers believe that the submitters have the best information on
the common identity of their benchmarks and therefore partition each
division based on the bottom-level directory imposed by each submitter.
These partitions are referred to as \emph{families}.

\header{Benchmark selection.} \label{benchmark-selection}
%
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks \textbf{except}
the \challtrack, the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The competition organizers will
    remove all benchmarks that were solved by all solvers (including the
        non-competitive solvers) in less than one second in the 2018 SMT
        competition.
\item \emph{Cap the number of instances in a division.} The competition
  organizers will limit the number of benchmarks in a division as
  follows:
  \begin{enumerate}
  \item If a division contains less than 300 instances, all
        the instances will selected.
  \item If a division contains between 300 and 600 instances,
        a selection of 300 instances from the set will be selected.
  \item If a division contains more than 600 instances, 50\% of
        the benchmarks will be selected.
  \end{enumerate}
\item \emph{\ucoretrack{}.} In addition, for the \ucoretrack{}, all
  benchmarks with a single assertion will be removed.
\end{enumerate}
%
The selection process in cases (b) and (c) above will guarantee the
inclusion of new benchmarks by first picking randomly one benchmark from
each new benchmark family.  The rest of the benchmarks will be chosen
randomly from the remaining benchmarks using a uniform distribution.
%
The culling script will be publicly available and will use the same
random seed as the rest of the competition.  The set of benchmarks
selected for the competition will be published when the competition
begins.

>>>>

\header{Benchmark Selection.}
This track will run on all \emph{unsatisfiable} benchmarks from the \maintrack,
modified to use named top-level assertions of the form \akey{(assert (! t
:named f ))}.
\todo{what if removing all benchmarks with one assertion doesn't leave enough benchmarks in a division?}

@@

\header{Division}
Within each track there are multiple divisions, and each division selects
benchmarks from a specific SMT-LIB logic in the SMT-LIB benchmark library.

@@

\header{Benchmark sources.}
Benchmarks for each division will be drawn from the SMT-LIB benchmark library.
The \maintrack will use a subset of all \emph{non-incremental} benchmarks and
the \inctrack will use a subset of all \emph{incremental} benchmarks. The
\challtrack will use all incremental and non-incremental benchmarks dedicated
to this track by their submitters. The \ucoretrack will use all unsatisfiable
\maintrack benchmarks, modified to use named top-level assertions.  The
\mvaltrack will use all satisfiable \maintrack benchmarks from the QF\_BV
division.

\header{New benchmarks.}
The deadline for submission of new benchmarks is {\bf March~1, 2019}.
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf May~1, 2019}.  The SMT-LIB
maintainers intend to make a new release of the benchmark library
publicly available on or close to this date.

\header{Benchmark demographics.}
The set of all SMT-LIB benchmarks in a given division can be naturally
partitioned to sets containing benchmarks that are similar from the user
community perspective.  Such benchmarks could all come from the same
application domain, be generated by the same tool, or have some other
obvious common identity.
%
The organizers try to identify a meaningful partitioning based on the
directory hierarchy in SMT-LIB.  In many cases the hierarchy consists of
the top-level directories each corresponding to a submitter, who has
further imposed a hierarchy on the benchmarks.
%
The organizers believe that the submitters have the best information on
the common identity of their benchmarks and therefore partition each
division based on the bottom-level directory imposed by each submitter.
These partitions are referred to as \emph{families}.

\header{Benchmark selection.} \label{benchmark-selection}
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In \textbf{all} tracks \textbf{except}
the \challtrack, the following selection process will be used.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The organizers will remove all
  benchmarks that were solved by all solvers (including non-competitive
  solvers) in less than one second in 2018.
\item \emph{\ucoretrack.} In addition, for the \ucoretrack, all
  benchmarks with a single assertion will be removed.
\item \emph{Cap the number of instances in a division.} The organizers will
  limit the number of benchmarks in a division based on the size of the
  corresponding logic in SMT-LIB as follows:
  \begin{enumerate}
  \vspace{-1ex}
    \item \label{bench-sel-300} If a logic contains less than 300 instances,
      all instances will selected.
  \item \label{bench-sel-600} If a logic contains between 300 and 600
    instances, a subset of 300 instances from the set will be selected.
  \item \label{bench-sel-more} If a logic contains more than 600 instances,
    50\% of the benchmarks will be selected.
  \end{enumerate}
\end{enumerate}
%
The selection process in cases \ref{bench-sel-600} and \ref{bench-sel-more}
above will guarantee the inclusion of new benchmarks by first picking randomly
one benchmark from each new benchmark family.  The rest of the benchmarks will
be chosen randomly from the remaining benchmarks using a uniform distribution.
%
The benchmark selection script will be publicly available at \rem{link tba} and
will use the same random seed as the rest of the competition.  The set of
benchmarks selected for the competition will be published when the competition
begins.
